PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-04-27 paper/ms.tex
minor update

We begin in Section~\ref{sec:observations} by describing newly
available observations from TESS \citep{ricker_transiting_2015} and
Gaia \citep{gaia_collaboration_gaia_2018}.  The TESS lightcurve shows
two different periodic signals, which we analyze in
Section~\ref{sec:tess}.
The Gaia data, analyzed in Section~\ref{sec:gaia}, show that
\ptfo\ is a photometric binary, and suggest it also an astrometric binary.
We discuss the pieces of the puzzle
in Section~\ref{sec:discussion}, and summarize the situation in
Section~\ref{sec:conclusions}.

@@

Minor differences in our approaches are that \citet{koen_2020}
interprets the ``out of dip'' signal to potentially show multiple
dips, while our BIC-based model comparison did not indicate the need
for additional harmonics after fitting for the largest dip and two
harmonics at $P_{\rm s}$ (Table~1). Our analysis emphasized the
agreement between the TESS dip ephemeris and that from
\citet{tanimoto_evidence_2020}.  \citet{koen_2020} however made a
clearer case for testing the binarity hypothesis using interferometric
imaging and high-precision radial velocities.
\\
\\
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank D.~Fabrycky for helpful tidal evolution calculations
that were eventually omitted.
%
We thank the Heising-Simons Foundation for their generous support of this work.
%
\ptfo\ was included on the TESS ``short-cadence'' target list thanks to the
Guest Investigator programs of S.\ Czesla and C.\ Huang (G011128 and
G011132 respectively).
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

>>>>

We begin in Section~\ref{sec:observations} by describing newly
available observations from TESS \citep{ricker_transiting_2015} and
Gaia \citep{gaia_collaboration_gaia_2018}.  The TESS lightcurve shows
two different periodic signals, which we analyze in
Section~\ref{sec:tess}.
The Gaia data, analyzed in Section~\ref{sec:gaia}, show that
\ptfo\ is a photometric binary, and suggest it also an astrometric binary.
We discuss the pieces of the puzzle
in Section~\ref{sec:discussion}, and summarize the situation in
Section~\ref{sec:conclusions}.
We comment on the
concurrent study by \citet{koen_2020} in postscript.

@@

Minor differences in our approaches are that \citet{koen_2020}
interprets the ``out of dip'' signal to potentially show multiple
dips, while our BIC-based model comparison did not indicate the need
for additional harmonics after fitting for the largest dip and two
harmonics at the shorter period (Table~1). Our analysis emphasized the
agreement between the TESS dip ephemeris and that from
\citet{tanimoto_evidence_2020}.  \citet{koen_2020} however made a
clearer case for testing the binarity hypothesis using interferometric
imaging and high-precision radial velocities.
\\
\\
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank D.~Fabrycky for helpful tidal evolution calculations
that were eventually omitted.
%
We thank the Heising-Simons Foundation for their generous support of this work.
%
\ptfo\ was included on the TESS ``short-cadence'' target list thanks to the
Guest Investigator programs of S.\ Czesla and C.\ Huang (G011128 and
G011132 respectively).
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%
